---
title: "Exploratory Data Analysis - Cycle 03"
author: "Cleverson Oliveira"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output:
  html_document:
    highlight: textmate
    logo: logo.png
    theme: jou
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
    df_print: paged
    code_folding: hide
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Imports

```{r imports}
library(tidyverse)
library(janitor)
library(skimr)
library(gtsummary)
library(kableExtra)
library(summarytools)
library(gridExtra)
```

# Data Collection

You can also embed plots, for example:

```{r collection, echo=FALSE}
df3 <- readRDS("df2.rds")
View(df3)
glimpse(df3)
```

# Column Description

```{r, echo=FALSE}
variables <- df3 %>% names()
description <- c(
  "Unique ID for the customer",
  "Gender of the customer",
  "Age of the customer",
  "Customer has DL (yes/no)",
  "Unique code for the region of the customer",
  "Customer already has Vehicle Insurance (yes/no)",
  "Age of the Vehicle",
  "Customer got his/her vehicle damaged in the past (yes/no)",
  "The amount customer needs to pay as premium in the year",
  "Anonymized Code for the channel of outreaching to the customer ie. Different Agents, Over Mail, Over Phone, In Person, etc.",
  "Number of Days, Customer has been associated with the company",
  "Customer is interested in car insurance (yes/no)"
)

df_description <- tibble(variables = variables,
                  description = description)

kable(df_description, format = "html") %>% 
kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

# Hypothesis Validation

### H1) Older customers are more likely to be interested in car insurance.

```{r, echo=FALSE}
# Boxplot
age_boxplot <- df3 %>% 
      ggplot(aes(x=response, y=age)) + 
      stat_boxplot(geom='errorbar', width=0.6) +
      geom_boxplot(aes(fill=response), show.legend = FALSE) + 
      labs(title = "Age vs. Response Comparison", y = "Age", x = "Response") + 
      theme_bw()
age_boxplot
ggsave("age_boxplot.jpg", plot = age_boxplot, width=4, height=6)

# Hystogram
age_plot <- df3 %>% 
      ggplot(aes(x=age)) + 
      geom_histogram(binwidth=1, color="gray", fill="navy") + 
      facet_wrap(vars(response), nrow=2, scales="free_y") +
      labs(y="Number of Clients") +
      ggtitle("Age Distribution")
age_plot
# To save a figure file
ggsave("age_plot.jpg", plot = age_plot, width=4, height=6)
```

```{r, echo=FALSE}
# Descriptive Statistics
df3 %>% 
  select(age, response) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Young people seem to be less interested in car insurance. The median age of interested customers is 43 years old (AIQ: 35.51), while the median age of uninterested customers is 34 years old (AIQ: 24.49).

### H2) Women are probably more interested in car insurance.

```{r, echo=FALSE}
gender_plot <- df3 %>% 
  select(response, gender) %>% 
  ggplot(aes(x = response)) +
  geom_bar(aes(fill=gender), position = 'dodge') +
  labs(title = "Gender vs. Response", x = "Response", y = "Number of customers") +
    theme_bw()
gender_plot
ggsave("gender_plot.jpg", plot = gender_plot, width=4, height=6)
```

```{r, echo=FALSE}
df3 %>% 
  select(response, gender) %>% 
  tbl_summary(by = response)
```

#### Of the customers interested in car insurance, 61% were men and 39% were women. Therefore this hypothesis is FALSE. Although gender and response are statistically significant, i. e., are related.

### H3) Customers having newer cars are more likely to be interested in car insurance.

```{r, echo=FALSE}
car_age_plot <- gender_plot <- df3 %>% 
     select(response, vehicle_age) %>% 
        ggplot(aes(x = response)) +
        # bar chart for categorical label
        geom_bar(aes(fill = vehicle_age), position = 'dodge') +
        labs(title = "Vehicle Age vs. Response", x = "Response", y = "Number of customers") +
        theme_bw()
car_age_plot
ggsave("car_age_plot.jpg", plot = car_age_plot, width=4, height=6)
```

```{r, echo=FALSE}
df3 %>% 
  select(response, vehicle_age) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Customers who own a car between 1 and 2 years are more likely to be interested in the car insurance (75%). While only 15% of the interested customers have new car. This hypothesis is FALSE.

### H4) Customers with previous car damage are more likely to accept auto insurance.

```{r, echo=FALSE}
car_damage_plot <- gender_plot <- df3 %>% 
  select(response, vehicle_damage) %>% 
  ggplot(aes(x = response)) +
  # bar chart for categorical label
  geom_bar(aes(fill = vehicle_damage), position = 'dodge') +
labs(title = "Vehicle Damage vs. Response", x = "Response", y = "Number of customers") +
    theme_bw()
car_damage_plot
ggsave("car_damage_plot.jpg", plot = car_damage_plot, width=4, height=6)
```

```{r, echo=FALSE}
df3 %>% 
  select(response, vehicle_damage) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Customers with previous car damage are more likely to be interested in car insurance, as 98% said yes.

### H5) Customers with previous car insurance are more likely to accept car insurance.

```{r, echo=FALSE}
car_insurance_plot <- gender_plot <- df3 %>% 
    select(response, previously_insured) %>% 
      ggplot(aes(x = response)) +
      # bar chart for categorical label
      geom_bar(aes(fill = previously_insured), position = 'dodge') +
      labs(title = "Previously Insured vs. Response", x = "Response", y = "Number of customers") +
      theme_bw()
car_insurance_plot
ggsave("car_insurance_plot.jpg", plot = car_insurance_plot, width=4, height=6)
```

```{r, echo=FALSE}
df3 %>% 
  select(response, previously_insured) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Only 0.3% of customers interested in car insurance have car previously insured. FALSE

### H6) Interest in car insurance is greater among customers who have higher annual health insurance.

```{r, echo=FALSE}
# Boxplot
expenses_boxplot <- df3 %>% 
  ggplot(aes(x=response, y=health_annual_paid)) + 
  stat_boxplot(geom='errorbar', width=0.6) +
  geom_boxplot(aes(fill=response), show.legend = FALSE) + 
  labs(title = "Health Annual Paind vs. Response Comparison", y = "Annual Payment", x = "Response") + 
  theme_bw()
expenses_boxplot
ggsave("expenses_boxplot.jpg", plot = expenses_boxplot, width=4, height=6)

# Hystogram
expenses_plot <- df3 %>% 
  ggplot(aes(x=health_annual_paid)) + 
  geom_histogram(binwidth=10000, color="gray", fill="navy") + 
  facet_wrap(vars(response), nrow=2, scales="free_y") +
  labs(y="Number of Clients") +
  ggtitle("Expenses Distribution")
expenses_plot
# To save a figure file
ggsave("expenses_plot.jpg", plot = expenses_plot, width=4, height=6)
```

```{r, echo=FALSE}
df3 %>% 
  select(response, health_annual_paid) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Although the annual healthcare paid has proven to be significant, this hypothesis will be considered FALSE, but its outliers will be investigated, in the next cycle, for example. There are many similarities between the alternatives. There are to much similarities between the alternatives.

### H7) Customers who have had health insurance for longer are more likely to be interested in car insurance.

```{r, echo=FALSE}
# for numerical label
# Boxplot
days_boxplot <- df3 %>% 
  ggplot(aes(x=response, y=days_associated)) + 
  stat_boxplot(geom='errorbar', width=0.6) +
  geom_boxplot(aes(fill=response), show.legend = FALSE) + 
  labs(title = "Days Associated vs. Response Comparison", y = "Annual Payment", x = "Response") + 
  theme_bw()
days_boxplot
ggsave("days_boxplot.jpg", plot = days_boxplot, width=4, height=6)

# Hystogram
days_plot <- df3 %>% 
  ggplot(aes(x=days_associated)) + 
  geom_histogram(binwidth=30, color="gray", fill="navy") + 
  facet_wrap(vars(response), nrow=2, scales="free_y") +
  labs(y="Number of Clients") +
  ggtitle("Expenses Distribution")
days_plot
# To save a figure file
ggsave("days_plot.jpg", plot = days_plot, width=4, height=6)
```

```{r, echo=FALSE}
df3 %>% 
  select(response, days_associated) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### This hypothesis is false, basically interested customers and non-interested customers have the same amount of days associated. Yes (median: 154 days, IIQ: 82, 226); No (154 days, AIQ: 82, 227).

### Hypothesis Conclusion

```{r, echo=FALSE}
Hypothesis <- c(
  "H1) Older customers are more likely to be interested in car insurance.",
  "H2) Women are probably more interested in car insurance.",
  "H3) Customers having newer cars are more likely to be interested in car insurance.",
  "H4) Customers with previous car damage are more likely to accept auto insurance.",
"H5) Customers with previous car insurance are more likely to accept car insurance.",
"H6) Interest in car insurance is greater among customers who have higher annual health insurance.",
"H7) Customers who have had health insurance for longer are more likely to be interested in car insurance."
)

Conclusion <- c(
              "True",
              "False",
              "False",
              "True",
              "False",
              "False",
              "False"
              )

Relevance <- c(
              "High",
              "Medium",
              "High",
              "High",
              "High",
              "Low",
              "Low"
              )

hypothesis_table <- 
  tibble(Hypothesis, Conclusion, Relevance)

kable(hypothesis_table, format = "html") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped",
                            full_width = FALSE)
```

# 
