---
title: "Data Preparation and Feature Selection"
author: "Cleverson Oliveira"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output:
  html_document:
    highlight: textmate
    logo: logo.png
    theme: jou
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
    df_print: paged
    code_folding: hide
  pdf_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Imports

```{r, echo=FALSE}
#install.packages("devtools")
#devtools::install_github("ropensci/skimr")
#install.packages("gtsummary")
#install.packages("magick")
#install.packages("summarytools")
#install.packages("knitr")
#install.packages("kableExtra")
#devtools::install_github("kupietz/kableExtra")
#install.packages("gridExtra")
#install.packages("reshape2")
#install.packages("tidymodels")
#install.packages("randomForest")
#install.packages("tidyverse")
#install.packages("RcppEigen")
#install.packages("ranger")
#install.packages("xgboost")
#install.packages("kknn")
```

```{r, echo=FALSE}
library(dplyr)
library(tidyverse)
library(janitor)
library(gtsummary)
library(summarytools)
library(knitr)
library(kableExtra)
library(gridExtra)
library(readr)
library(ggplot2)
library(tidymodels)
library(randomForest)
```

# Data Collection

```{r collection, echo=FALSE}
df4 <- readRDS("df3.rds")
View(df4)
glimpse(df4)
```

# Column Description

```{r, echo=FALSE}
variables <- df4 %>% names()
description <- c(
  "Unique ID for the customer",
  "Gender of the customer",
  "Age of the customer",
  "Customer has DL (yes/no)",
  "Unique code for the region of the customer",
  "Customer already has Vehicle Insurance (yes/no)",
  "Age of the Vehicle",
  "Customer got his/her vehicle damaged in the past (yes/no)",
  "The amount customer needs to pay as premium in the year",
  "Anonymized Code for the channel of outreaching to the customer ie. Different Agents, Over Mail, Over Phone, In Person, etc.",
  "Number of Days, Customer has been associated with the company",
  "Customer is interested in car insurance (yes/no)"
)

df_description <- tibble(variables = variables,
       description = description)

kable(df_description, format = "html") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped",
                            full_width = FALSE)
```

# Data Preparation

Frequency encoding for policy_sales_channel

Target encoding for gender e region_code

## Target encoding

```{r, echo=FALSE}
gender_encoder <- df4 %>% 
  mutate(response_num = ifelse(response == "yes", 1, 0)) %>%
  group_by(gender) %>% 
  summarise(gender_num = mean(response_num, na.rm = TRUE))

region_encoder <- df4 %>% 
  mutate(response_num = ifelse(response == "yes", 1, 0)) %>%
  group_by(region_code) %>% 
  summarise(region_num = mean(response_num, na.rm = TRUE))

# save in RDS
saveRDS(gender_encoder, "gender_encoder.rds")
saveRDS(region_encoder, "region_encoder.rds")
```

## Frequency encoding

```{r, echo=FALSE}
policy_encoder <- df4 %>% 
  group_by(policy_sales_channel) %>% 
  # divide each category by the number of rows
  summarise(policy_num = n()/nrow(df4))

saveRDS(policy_encoder, "policy_encoder.rds")
```

### Building Encoder Function

```{r, echo=FALSE}
encoder_function <- function(df){
  df %>% 
  # add the new encoded columns and delete the original column
  left_join(gender_encoder) %>% 
  select(-gender) %>% 
  rename(gender = gender_num) %>% #View()
    
  left_join(region_encoder) %>% 
  select(-region_code) %>% 
  rename(region_code = region_num) %>% #View()
    
  left_join(policy_encoder) %>% 
  select(-policy_sales_channel) %>% 
  rename(policy_sales_channel = policy_num) #View()
} 
```

```{r, echo=FALSE}
saveRDS(encoder_function, "encoder_function.rds")
```

## Splitting data into train and test

```{r, echo=FALSE}
#encoder_function <- readRDS("encoder_function.rds")
df_preprocessed <- encoder_function(df4)
```

```{r, echo=FALSE}
set.seed(123)

df_split <- df_preprocessed %>% 
  initial_split(prop = 0.75, strata = response)

df_train <- df_split %>% 
  training()

df_test <- df_split %>% 
  testing()
```

### Check response proportions

```{r, echo=FALSE}
df_train %>% 
  select(response) %>% 
  tbl_summary(type = list(response ~ "categorical"))

df_test %>% 
  select(response) %>% 
  tbl_summary(type = list(response ~ "categorical"))
```

### Using tidymodels steps to continue the preprocessing

```{r, echo=FALSE}
df_recipe <- recipe(response ~.,
       data = df_train) %>% 
  step_normalize(age, days_associated) %>% 
  step_scale(health_annual_paid) %>% 
  step_dummy(all_nominal(), -all_outcomes())
```

### Applying the recipe

```{r, echo=FALSE}
df_train_prep <- df_recipe %>% 
  prep(df_train)
  #prep(training = df_train)

df_train_processed <- df_train_prep %>% 
  bake(df_train)
  #bake(new_data = df_train)
```

```{r, echo=FALSE}
df_test_processed <- df_train_prep %>% 
  bake(df_test)
  #bake(new_data = df_test)
```

# Feature Selection

```{r, echo=FALSE}
predictors <- df_train_processed %>% 
  select(-id, -response)

target <- df_train_processed$response
```

```{r, echo=FALSE}
start_time <- Sys.time()

rf_model <- randomForest(predictors, target, ntree = 10, importance = TRUE)

end_time <- Sys.time()

print(end_time - start_time)
```

### Show results

```{r, echo=FALSE}
importance(rf_model) %>% View()
```

```{r, echo=FALSE}
varImpPlot(rf_model)
```

In this first cycle we are going to select the seven most important variables according to the mean decrease gini

```{r, echo=FALSE}
importance(rf_model) %>% 
  as_tibble(rownames = "rowname") %>% 
  arrange(desc(MeanDecreaseGini)) %>%  # arrange the importance
  select(rowname) %>%  # select the names of columns
  slice(1:7) %>%  # get only the first seven
  pull()
```

```{r, echo=FALSE}
#Final dataset
#selected_columns <- c(
#  "age",
#  "vehicle_damage",
#  "days_associated",
#  "previously_insured",
#  "health_annual_paid",
#  "policy_sales_channel",
#  "region_code",
#  "response"
#)
#
#df_selected <- df4 %>% 
#  select(all_of(selected_columns))

saveRDS(df4, "df4.rds")
```
