---
title: "Data Science With R"
author: "Cleverson Oliveira"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output:
  html_document:
    highlight: textmate
    logo: logo.png
    theme: jou
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
    df_print: paged
    code_folding: hide
  pdf_document:
    toc: yes
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Imports

```{r, echo=FALSE}
#install.packages("devtools")
#devtools::install_github("ropensci/skimr")
#install.packages("gtsummary")
#install.packages("magick")
#install.packages("summarytools")
#install.packages("knitr")
#install.packages("kableExtra")
#devtools::install_github("kupietz/kableExtra")
#install.packages("gridExtra")
#install.packages("reshape2")
#install.packages("tidymodels")
#install.packages("randomForest")
#install.packages("tidyverse")
#install.packages("RcppEigen")
#install.packages("ranger")
#install.packages("xgboost")
#install.packages("kknn")
```

```{r, echo=FALSE}
library(dplyr)
library(tidyverse)
library(janitor)
library(gtsummary)
library(summarytools)
library(knitr)
library(kableExtra)
library(gridExtra)
library(readr)
library(ggplot2)
library(tidymodels)
library(randomForest)
```

# Data Collection

```{r, echo=FALSE}
df <- readr::read_csv("dataset/train.csv")
glimpse(df, width = 50)
```

# Data Cleaning

```{r, echo=FALSE}
df1 <- janitor::clean_names(df) %>% 
  
  rename(days_associated = vintage, 
         health_annual_paid = annual_premium) %>% 
  
  mutate(
    across(where(is.character), tolower),
    driving_license = ifelse(driving_license==1, "yes", "no"),
    previously_insured = ifelse(previously_insured==1, "yes", "no"),
    response = ifelse(response==1, "yes", "no"),
    vehicle_age = case_when(
      vehicle_age == "< 1 year" ~ "below_1_year",
      vehicle_age == "1-2 year" ~ "between_1_2_years",
      vehicle_age == "> 2 years" ~ "over_2_years"
    )
  ) %>% 
  
  mutate_if(is.character, as.factor) %>% 
  # Make sure yes is the first level of factor response
  mutate(response = factor(response, levels=c("yes", "no")),
    previously_insured = factor(previously_insured, levels=c("yes", "no")),
    driving_license = factor(driving_license, levels=c("yes", "no")),
    vehicle_damage = factor(vehicle_damage, levels=c("yes", "no")))

glimpse(df1)

saveRDS(df1, "df_cleaned.rds")
```

```{r, echo=FALSE}
#, eval=FALSE, echo=FALSE}
# checking categorical levels
df1 %>% 
  select(-id) %>% 
  tbl_summary(
    type = list(response ~ "categorical",
                driving_license~ "categorical",
                previously_insured~ "categorical",
                vehicle_damage~ "categorical"),
    digits = list(all_categorical()~c(0, 2))
  )
```

```{r, eval=FALSE, echo=FALSE}
df %>% names()
df1 %>% names()
```

## Data Types

```{r estrutura, eval=FALSE, echo=FALSE}
str(df)
```

```{r, echo=FALSE}
variable_classes <- tibble(variables=names(df1),
       type=unlist(lapply(df1, class)))
variable_classes
```

# Column Description

```{r, echo=FALSE}
variables <- df1 %>% names()
description <- c(
  "Unique ID for the customer",
  "Gender of the customer",
  "Age of the customer",
  "Customer has DL (yes/no)",
  "Unique code for the region of the customer",
  "Customer already has Vehicle Insurance (yes/no)",
  "Age of the Vehicle",
  "Customer got his/her vehicle damaged in the past (yes/no)",
  "The amount customer needs to pay as premium in the year",
  "Anonymized Code for the channel of outreaching to the customer ie. Different Agents, Over Mail, Over Phone, In Person, etc.",
  "Number of Days, Customer has been associated with the company",
  "Customer is interested in car insurance (yes/no)"
)

df_description <- tibble(variables = variables,
       description = description)

kable(df_description, format = "html") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped",
                            full_width = FALSE)
```

# Descriptive Statistics

```{r, echo=FALSE}
df_cleaned <- readRDS("df_cleaned.rds")
glimpse(df_cleaned)
```

## Check data structure

```{r, echo=FALSE}
skimr::skim(df_cleaned)
```

## Numerical Statistics

```{r, echo=FALSE}
num_attributes <- df_cleaned %>% 
  select(age, health_annual_paid, days_associated)

desciptive_tab <- descr(num_attributes, style="rmarkdown") %>%  round(2)

kable(data.frame(desciptive_tab), format="html") %>% kableExtra::kable_styling(bootstrap_options = "striped", full_width=FALSE)
```

# Visualization

## Numerical Attributes

```{r, echo=FALSE}
num_attributes <- df_cleaned %>% 
  select(age, health_annual_paid, days_associated)

age_plt <- num_attributes %>% 
  ggplot(aes(x=age)) + 
  geom_histogram(aes(y=after_stat(density)), binwidth=1, color="gray", fill="lightblue", alpha=0.5) + 
  geom_density(color="blue") +
  labs(x="Age", y="Density", title="Customer Age Distribution") + 
  theme_minimal()
```

```{r, echo=FALSE}
paid_plt <- num_attributes %>% 
  ggplot(aes(x=health_annual_paid)) + 
  geom_histogram(aes(y=after_stat(density)), binwidth=10000, color="gray", fill="lightblue", alpha=0.5) + 
  geom_density(color="blue") +
  labs(x="Health Annual Paid", y="Density", title="Customer Payments \nDistribution") + 
  theme_minimal()
```

```{r, echo=FALSE}
days_plt <- num_attributes %>% 
  ggplot(aes(x=days_associated)) + 
  geom_histogram(aes(y=after_stat(density)), binwidth=5, color="gray", fill="lightblue", alpha=0.5) + 
  geom_density(color="blue") +
  labs(x="Health Annual Paid", y="Density", title="Customer Days \nAssociated Distribution") + 
  theme_minimal()
```

```{r, echo=FALSE}
grid.arrange(age_plt, paid_plt, days_plt, ncol=3)
```

## Categorical Attributes

```{r, echo=FALSE}
num_names <- names(num_attributes)
cat_attributes <- df_cleaned %>% 
  select(-id, -one_of(num_names))
```

```{r, echo=FALSE}
gender_plt <- cat_attributes %>% 
  ggplot(aes(x=gender)) +
  geom_bar(aes(fill=gender)) +
  labs(x="Gender", y="Quantity", title="Customers Gender") + 
  theme_minimal()

driving_license_plt <- cat_attributes %>% 
  ggplot(aes(x=driving_license)) +
  geom_bar(aes(fill=driving_license)) +
  labs(x="Driving License", y="Quantity", title="Customers \nDriving License") +
  theme_minimal()

region_code_plt <- cat_attributes %>% 
  ggplot(aes(x=region_code)) +
  geom_bar(aes(fill=factor(region_code)), show.legend = FALSE) +
  labs(x="Region Code", y="Quantity", title="Customers \nRegion Code") + 
  theme_minimal()

previously_insured_plt <- cat_attributes %>% 
  ggplot(aes(x=previously_insured)) +
  geom_bar(aes(fill=previously_insured)) +
  labs(x="Previously Insured", y="Quantity", title="Customers \nPreviously Insured") + 
  theme_minimal()

vehicle_age_plt <- cat_attributes %>% 
  ggplot(aes(x=vehicle_age)) +
  geom_bar(aes(fill=vehicle_age)) +
  labs(x="Vehicle Age", y="Quantity", title="Customers \nVehicle Age") + 
  theme_minimal()

vehicle_damage_plt <- cat_attributes %>% 
  ggplot(aes(x=vehicle_damage)) +
  geom_bar(aes(fill=vehicle_damage)) +
  labs(x="Vehicle Damage", y="Quantity", title="Customers \nVehicle Damage") + 
  theme_minimal()

policy_sales_channel_plt <- cat_attributes %>% 
  ggplot(aes(x=policy_sales_channel)) +
  geom_bar(aes(fill=factor(policy_sales_channel)), show.legend = FALSE) +
  labs(x="Police Sales Channel", y="Quantity", title="Customers Police \nSales Channel") + 
  theme_minimal()

response_plt <- cat_attributes %>% 
  ggplot(aes(x=response)) +
  geom_bar(aes(fill=response)) +
  labs(x="Response", y="Quantity", title="Customers Response") + 
  theme_minimal()
```

```{r, echo=FALSE}
grid.arrange(gender_plt, driving_license_plt, region_code_plt, previously_insured_plt, vehicle_age_plt, vehicle_damage_plt, policy_sales_channel_plt, response_plt, ncol=2, nrow=4)
```

# Hypothesis Validation

```{r, echo=FALSE}
df_cleaned <- readRDS("df_cleaned.rds")
```

### H1) Older customers are more likely to be interested in car insurance.

```{r, echo=FALSE}
# Boxplot
age_boxplot <- df_cleaned %>% 
  ggplot(aes(x=response, y=age)) + 
  stat_boxplot(geom='errorbar', width=0.6) +
  geom_boxplot(aes(fill=response), show.legend = FALSE) + 
  labs(title = "Age vs. Response Comparison", y = "Age", x = "Response") + 
  theme_bw()

ggsave("age_boxplot.jpg", plot = age_boxplot, width=4, height=6)

# Hystogram
age_plot <- df_cleaned %>% 
  ggplot(aes(x=age)) + 
  geom_histogram(binwidth=1, color="gray", fill="navy") + 
  facet_wrap(vars(response), nrow=2, scales="free_y") +
  labs(y="Number of Clients") +
  ggtitle("Age Distribution")

# To save a figure file
ggsave("age_plot.jpg", plot = age_plot, width=4, height=6)
```

```{r, echo=FALSE}
# Descriptive Statistics
df_cleaned %>% 
  select(age, response) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Young people seems to be less likely interested in car insurance. The median age for interested customers is 43 years (IQR: 35, 51), while the median for non-interested customers is 34 years (IQR: 24, 49). \## explain the p-value

### H2) Women are likely more interested in car insurance 🟥

```{r, echo=FALSE}
gender_plot <- df_cleaned %>% 
  select(response, gender) %>% 
  ggplot(aes(x = response)) +
  geom_bar(aes(fill=gender), position = 'dodge') +
  labs(title = "Gender vs. Response", x = "Response", y = "Number of customers") +
    theme_bw()
gender_plot
ggsave("gender_plot.jpg", plot = gender_plot, width=4, height=6)
```

```{r, echo=FALSE}
df_cleaned %>% 
  select(response, gender) %>% 
  tbl_summary(by = response)
```

#### For customers interested in car insurance, 61% were men, and 39% were women. So this hypothesis is FALSE. Although, gender and response are statistically significant, i. e., are related.

### H3) Customers having newer cars are more likely to be interested in car insurance

```{r, echo=FALSE}
car_age_plot <- gender_plot <- df_cleaned %>% 
  select(response, vehicle_age) %>% 
  ggplot(aes(x = response)) +
  # bar chart for categorical label
  geom_bar(aes(fill = vehicle_age), position = 'dodge') +
labs(title = "Vehicle Age vs. Response", x = "Response", y = "Number of customers") +
    theme_bw()
car_age_plot
ggsave("car_age_plot.jpg", plot = car_age_plot, width=4, height=6)
```

```{r, echo=FALSE}
df_cleaned %>% 
  select(response, vehicle_age) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Customers who own a car between 1 and 2 years are more likely to be interested in the car insurance (75%). While, only 15% of the interested customers have new car.

### H4) Customer with previous car damage are more likely to accept car insurance ✅

```{r, echo=FALSE}
car_damage_plot <- gender_plot <- df_cleaned %>% 
  select(response, vehicle_damage) %>% 
  ggplot(aes(x = response)) +
  # bar chart for categorical label
  geom_bar(aes(fill = vehicle_damage), position = 'dodge') +
labs(title = "Vehicle Damage vs. Response", x = "Response", y = "Number of customers") +
    theme_bw()
car_damage_plot
ggsave("car_damage_plot.jpg", plot = car_damage_plot, width=4, height=6)
```

```{r, echo=FALSE}
df_cleaned %>% 
  select(response, vehicle_damage) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Customers with previous car damage are more likely to be interested in car insurance, as 98% said yes.

### H5) Customers with previous car insurance are more likely to accept car insurance :

```{r, echo=FALSE}
car_insurance_plot <- gender_plot <- df_cleaned %>% 
  select(response, previously_insured) %>% 
  ggplot(aes(x = response)) +
  # bar chart for categorical label
  geom_bar(aes(fill = previously_insured), position = 'dodge') +
labs(title = "Previously Insured vs. Response", x = "Response", y = "Number of customers") +
    theme_bw()
car_insurance_plot
ggsave("car_insurance_plot.jpg", plot = car_insurance_plot, width=4, height=6)
```

```{r, echo=FALSE}
df_cleaned %>% 
  select(response, previously_insured) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### Only 0.3& of customers interested in car insurance have car previously insured

### H6) Interest in car insurance is greater in customers which have higher annual health insurance 🟥

```{r, echo=FALSE}
# Boxplot
expenses_boxplot <- df_cleaned %>% 
  ggplot(aes(x=response, y=health_annual_paid)) + 
  stat_boxplot(geom='errorbar', width=0.6) +
  geom_boxplot(aes(fill=response), show.legend = FALSE) + 
  labs(title = "Health Annual Paind vs. Response Comparison", y = "Annual Payment", x = "Response") + 
  theme_bw()
expenses_boxplot
ggsave("expenses_boxplot.jpg", plot = expenses_boxplot, width=4, height=6)

# Hystogram
expenses_plot <- df_cleaned %>% 
  ggplot(aes(x=health_annual_paid)) + 
  geom_histogram(binwidth=10000, color="gray", fill="navy") + 
  facet_wrap(vars(response), nrow=2, scales="free_y") +
  labs(y="Number of Clients") +
  ggtitle("Expenses Distribution")
expenses_plot
# To save a figure file
ggsave("expenses_plot.jpg", plot = expenses_plot, width=4, height=6)
```

```{r, echo=FALSE}
df_cleaned %>% 
  select(response, health_annual_paid) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

Although the health annual paid showed to be significant, we consider this hyphotesis false and will further investigate the outliers, in he next cycle for example.

### H7) Customers who has health insurance for LONGER are more likely to be interested in car insurance 🟥

```{r, echo=FALSE}
# for numerical label
# Boxplot
days_boxplot <- df_cleaned %>% 
  ggplot(aes(x=response, y=days_associated)) + 
  stat_boxplot(geom='errorbar', width=0.6) +
  geom_boxplot(aes(fill=response), show.legend = FALSE) + 
  labs(title = "Days Associated vs. Response Comparison", y = "Annual Payment", x = "Response") + 
  theme_bw()
days_boxplot
ggsave("days_boxplot.jpg", plot = days_boxplot, width=4, height=6)

# Hystogram
days_plot <- df_cleaned %>% 
  ggplot(aes(x=days_associated)) + 
  geom_histogram(binwidth=30, color="gray", fill="navy") + 
  facet_wrap(vars(response), nrow=2, scales="free_y") +
  labs(y="Number of Clients") +
  ggtitle("Expenses Distribution")
days_plot
# To save a figure file
ggsave("days_plot.jpg", plot = days_plot, width=4, height=6)
```

```{r, echo=FALSE}
df_cleaned %>% 
  select(response, days_associated) %>% 
  tbl_summary(by=response) %>% 
  add_p()
```

#### This Hypothesis is false, basically the interested customers and non-interested customers have the same amount of days associated. Yes(median:154 days, IQR: 82, 226); No (154 days, IQR: 82, 227).

### Hypothesis Conclusion

```{r, echo=FALSE}
hypothesis <- c(
  "H1) OLDER customers are more likely to be interested in car insurance",
  "H2) Women are likely more interested in car insurance",
  "H3) Customers having newer cars are more likely to be interested in car insurance",
  "H4) Customer with previous car damage are more likely to accept car insurance",
"H5) Customers with previous car insurance are more likely to accept car insurance",
"H6) Interest in car insurance is greater in customers which have higher annual health insurance",
"H7) Customers who has health insurance for LONGER are more likely to be interested in car insurance"
)

conclusion <- c(
  "True",
  "False",
  "False",
  "True",
  "False",
  "False",
  "False"
  
)

relevance <- c(
  "High",
  "Medium",
  "High",
  "High",
  "High",
  "Low",
  "Low"
)

hypothesis_table <- 
  tibble(hypothesis, conclusion, relevance)

kable(hypothesis_table, format = "html") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped",
                            full_width = FALSE)
```

# Multivariable Analysis

### Correlation Matrix

```{r, echo=FALSE}
correlation_matrix <- df_cleaned %>% 
  select(age, days_associated, health_annual_paid) %>% 
  cor() %>% 
  round(3)
```

### Visualization

```{r, echo=FALSE}
library(reshape2)

melted_correlation <- melt(correlation_matrix)

matrix_correlation_plot <- ggplot(melted_correlation, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() + 
  geom_text(aes(Var1, Var2, label = value)) + 
  scale_fill_gradient2(low = "blue", high = "red", limit = c(-1,1), name = "Correlation") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.background = element_blank())

matrix_correlation_plot

ggsave("matrix_correlation_plot.jpg", matrix_correlation_plot, width = 8, height = 4)
```

There is no high correlation between numerical variables

# Data Preparation

Frequency encoding for policy_sales_channel

Target encoding for gender e region_code

## Target encoding

```{r, echo=FALSE}
gender_encoder <- df_cleaned %>% 
  mutate(response_num = ifelse(response == "yes", 1, 0)) %>%
  group_by(gender) %>% 
  summarise(gender_num = mean(response_num, na.rm = TRUE))

region_encoder <- df_cleaned %>% 
  mutate(response_num = ifelse(response == "yes", 1, 0)) %>%
  group_by(region_code) %>% 
  summarise(region_num = mean(response_num, na.rm = TRUE))

# save in RDS
saveRDS(gender_encoder, "gender_encoder.rds")
saveRDS(region_encoder, "region_encoder.rds")
```

## Frequency encoding

```{r, echo=FALSE}
policy_encoder <- df_cleaned %>% 
  group_by(policy_sales_channel) %>% 
  summarise(policy_num = n()/nrow(df_cleaned))

saveRDS(policy_encoder, "policy_encoder.rds")
```

### Using the created encoders in the dataset

```{r, echo=FALSE}
encoder_function <- function(df){
  df %>% 
  left_join(gender_encoder) %>% 
  select(-gender) %>% 
  rename(gender = gender_num) %>% 
  left_join(region_encoder) %>% 
  select(-region_code) %>% 
  rename(region_code = region_num) %>% 
  left_join(policy_encoder) %>% 
  select(-policy_sales_channel) %>% 
  rename(policy_sales_channel = policy_num)
}
```

```{r, echo=FALSE}
saveRDS(encoder_function, "encoder_function.rds")
```

## Splitting into train and test datasets

```{r, echo=FALSE}
encoder_function <- readRDS("encoder_function.rds")
df_preprocessed <- encoder_function(df_cleaned)
```

```{r, echo=FALSE}
set.seed(123)

df_split <- df_preprocessed %>% 
  initial_split(prop = 0.75, strata = response)

df_train <- df_split %>% 
  training()

df_test <- df_split %>% 
  testing()
```

### Check response proportions

```{r, echo=FALSE}
df_train %>% 
  select(response) %>% 
  tbl_summary(type = list(response ~ "categorical"))

df_test %>% 
  select(response) %>% 
  tbl_summary(type = list(response ~ "categorical"))
```

### Using tidymodels steps to continue the preprocessing

```{r, echo=FALSE}
df_recipe <- recipe(response ~.,
       data = df_train) %>% 
  step_normalize(age, days_associated) %>% 
  step_scale(health_annual_paid) %>% 
  step_dummy(all_nominal(), -all_outcomes())
```

### Applying the recipe

```{r, echo=FALSE}
df_train_prep <- df_recipe %>% 
  prep(trining = df_train)

df_train_processed <- df_train_prep %>% 
  bake(new_data = df_train)
```

```{r, echo=FALSE}
df_test_processed <- df_train_prep %>% 
  bake(new_data = df_test)
```

# Feature Selection

```{r, echo=FALSE}
predictors <- df_train_processed %>% 
  select(-id, -response)

target <- df_train_processed$response
```

```{r, echo=FALSE}
start_time <- Sys.time()

rf_model <- randomForest(predictors, target, ntree = 10, importance = TRUE)

end_time <- Sys.time()

print(end_time - start_time)
```

### Show results

```{r, echo=FALSE}
importance(rf_model) %>% View()
```

```{r, echo=FALSE}
varImpPlot(rf_model)
```

In tgis first cycle we are going to select the seven most importatnt vaiables according to the mean decrease gini

```{r, echo=FALSE}
importance(rf_model) %>% 
  as_tibble(rownames = "rowname") %>% 
  arrange(desc(MeanDecreaseGini)) %>% 
  select(rowname) %>% 
  slice(1:7) %>% 
  pull()
```

```{r, echo=FALSE}
#Final dataset
selected_columns <- c(
  "age",
  "vehicle_damage",
  "days_associated",
  "previously_insured",
  "health_annual_paid",
  "policy_sales_channel",
  "region_code",
  "response"
)

df_selected <- df_cleaned %>% 
  select(all_of(selected_columns))

saveRDS(df_selected, "df_selected.rds")
```
